Classless Java

### 2015-09-16 paper/sections/Formalization.tex
Attempt to grammar inserted
syntax fix
Expression typing, with comments

\section{Formal Semantics}\label{sec:typesafety}
Yanlin and Haoyuan

@@

>>>>

\section{Formal Semantics}\label{sec:typesafety}
\marco{Tentative Grammar ClassLessJava}

\begin{figure}[h]
\begin{grammar}
\production{
\e
}{
  \x\mid\MCall\e\m\es\mid\MCall{\C}\m\es\mid\MCall{\C\QM{.super}}\m\es\mid\obj
  }{expressions}\\
\production{
\obj
}{
\QM{new}\C\oR\cR\oC\T_1\f_1\QM;\ldots\T_k\f_k\QM;
\mh_1\oC\QM{return}\e_1\QM{;}\!\cC
\ldots
\mh_n\oC\QM{return}\e_n\QM{;}\!\cC
\cC
  }{object creation}\\
\production{
\metaVar{I}
}{
 \ann\ \QM{interface} \C_0\QM{extends}\C_1\ldots\C_k \oC\method_1\ldots\method_n\cC
  }{interface declaration}\\
\production{
\method
}{
 \QM{static}\mh\oC\QM{return}\e\QM{;}\!\cC
\mid 
\QM{default}\mh\oC\QM{return}\e\QM{;}\cC
\mid
\mh\QM{;}
  }{method declaration}\\
\production{
\mh
}{
 \T_0 \m  \oR\T_1\x_1\ldots\T_n\x_n\cR
  }{method header}\\
\production{
\ann
}{
  \mixinAnn|\emptyset
  }{annotations}\\
\end{grammar}
\caption{Grammar of ClassLess Java}
\label{Grammar}
\end{figure}

In Figure~\ref{Grammar} we show the syntax of ClassLess Java.

To be compatible with java, the concrete syntax for an interface declaration with empty supertype list $\C_1\ldots\C_k$ would also omit the \Q@extends@ keyword.

Yanlin and Haoyuan

@@

Expression Typing:

\[
\inferrule{}{\Gamma \vdash x \in \Gamma(x)} \quad \textsc{(T-Var)}
\]

\[
\inferrule{\Gamma \vdash e_0 \in C_0 \\ 
  \textsf{mtype}(m,C_0) = \overline{D} \to E \\ 
  \Gamma \vdash \overline{e} \in \overline{C} \\
  \overline{C} <: \overline{D} }
{ \Gamma \vdash e_0.m(\overline{e}) \in E }
\quad \textsc{(T-Invk)}
\]

\[
\inferrule{\textsf{mtype}(m,C) = \overline{D} \to E \\
\Gamma \vdash \overline{e} \in \overline{C} \\
\overline{C} <: \overline{D} \\
\textsf{mmodifier}(m,C) = \textbf{static} }
{\Gamma \vdash C.m(\overline{e}) \in E}
\quad \textsc{(T-StaticInvk)}
\]

\[
\inferrule{\textsf{mtype}(m,C) = \overline{D} \to E \\
\Gamma \vdash \overline{e} \in \overline{C} \\
\overline{C} <: \overline{D} \\
\textsf{checkSuper}(C.super.m(\overline{e}), A, C) \\\\
\text{\yanlin{check whether A <: C, where A is the enclosing interface of the
    expression}} }
{\Gamma \vdash C.\textbf{super}.m(\overline{e}) \in E}
\quad \textsc{(T-SuperInvk)}
\]
